Errorless irrationality: removing error-driven components from the inverse base-rate effect paradigm

### 2023-01-25 docs/manuscript.tex
finalise analysis

Nonetheless, in their Experiment 2, \citeA{johansen2007paradoxical} tried to observe the inverse base-rate effect both in a predictive-learning condition and in an observational-learning condition.
In the observational learning condition, category labels and features appeared together at the same time on the computer screen.
Their design involved disjoint cues where categories shared no features in common.
The canonical IBRE design involves a shared feature during training \cite{kruschke2001inverse, wills2014attention}.
According to the theories of the IBRE, this shared feature facilitates attentional relocation.
This attentional tuning in turn pushes responding towards the rare label.
In contrast, \citeA{johansen2007paradoxical} trained participants on $AB \to common$ and $C \to rare$.
Similarly, the $common$ category occurred three times as often as $rare$.
Their design was optimized to investigate the hypothesised asymmetric cognitive representation of the two categories.
As a result, the only instance when they observed a rare bias was when the common feature, $B$, presented in compound during training was paired with a rare, $C$, feature presented by itself during training.
This was taken as evidence for the asymmetric cognitive representation \cite{kruschke2001inverse} hypothesised to develop during training.

@@

We recruited 122 undergraduate students who completed the experiment for partial course credit.
Recruitment was done via the SONA recruitment system. \\

@@

We applied the same analysis and exclusion methods as in Experiment 1.
In addition, we also excluded participants whose mean reaction time fell one standard deviation, $\sigma = 519.96$ ms, below the group mean, $\mu = 1341.57$ ms.

@@

After exclusion, 59 participants made it into our analysis.
The group-level mean probabilities are shown in Table \ref{tab:results-exp2}.
The results are a qualitative and ordinal match to Experiment 1.
Participants showed a clear common preference for stimuli A, $M = 0.78$, 95\% HDI $[0.71, 0.85]$, $\mathrm{BF}_{10} = 7.72 \times 10^{8}$.

@@

Participants also showed a reliable rare preference on ambiguous BC trials, $M = 0.73$, 95\% HDI $[0.66, 0.80]$, $\mathrm{BF}_{10} = 581,370.03$.
This gives us a sufficient amount of evidence to conclude that we have observed the IBRE.

>>>>

@@

We recruited 171 undergraduate students who completed the experiment for partial course credit.
Recruitment was done via the SONA recruitment system. \\

@@

We applied the same analysis and exclusion methods as in Experiment 1.

@@

After exclusion, 86 participants made it into our analysis.
The group-level mean probabilities are shown in Table \ref{tab:results-exp2}.
The results are a qualitative and ordinal match to Experiment 1.
Participants showed a clear common preference for stimuli A, $M_{A} = 0.78$, 95\% HDI $[0.73, 0.83]$, $\mathrm{BF}_{10} = 5.37 \times 10^{13}$.

@@

Participants also showed a reliable rare preference on ambiguous BC trials, $M_{BC} = 0.73$, 95\% HDI $[0.67, 0.79]$, $\mathrm{BF}_{10} = 8.12 \times 10^{8}$.
This gives us a sufficient amount of evidence to conclude that we have observed the IBRE.
